\documentclass[12pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[scale=1, top = 4cm, bottom = 3cm, left = 1.5cm, right = 1.5cm]{geometry}
\recomputelengths

\moderncvtheme[black]{classic}
\firstname{STACEY}
\familyname{BRANDSMA}
\homepage{staceybrandsma.github.io/}
\social[linkedin]{stacey-brandsma/}
\social[github]{staceybrandsma}
\renewcommand{\labelitemi}{-}
\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault} 

\begin{document}

\vspace*{-4\baselineskip}
\makecvtitle
\vspace{-1.5\baselineskip}

\begin{flushright}
\textbf{\large senior data scientist \textasciitilde{} amgen} \\
\textbf{\large msc computer science, msc analytics, bsc biology} \\
\end{flushright}

I am a principal data scientist with several years of experience analyzing data and building and deploying machine learning models in large healthcare and biotech companies, with a passion for analyzing data to improve patient's lives.  
My area of interest and expertise is at the intersection between precision medicine, public health, and data science and their applications in improving patient care and treatments.  I have both a Master of Science in Computer Science and Master of Science in Analytics from Georgia Tech, in addition to my Bachelor of Science in Biology. \\

\section{Skills}
\cvitem{Programming:}{Python, R, SQL, Bash/Zsh, Git}
\cvitem{Methodologies:}{Machine Learning, Natural Language Processing, Image Analysis, Deep Learning, Big Data Analytics, Simulation, Bayesian Statistics, Business Analytics}
\cvitem{Engineering:}{AWS, Databricks}
\cvitem{Collaboration:}{Ideation and Project Development, Agile, Code Reviews, Pair Programming, Knowledge Sharing, Technical Presentations, Scrum, Software Testing, Jira, Confluence}
\cvitem{Areas of Expertise:}{Precision Medicine, Digital Health, BioPharma, Healthcare, Epidemiology, Public Health, Program Management, Research, Biomedical Informatics}

\section{Education}
\cventry{05/2024}{Master of Science in Computer Science}{Georgia Tech}{}{\textit{GPA: 4.0}}{
\begin{itemize}
    \item Artificial Intelligence, Deep Learning, Big Data for Healthcare, AI Ethics, Bayesian Statistics, Knowledge Based AI, Software Development Process, Human Computer Interaction, Machine Learning and Data Science Tools
    \item Independent Study: Predictive Modelling for Diabetes, Obesity, and Obstructive Sleep Apnea
\end{itemize} 
}
\cventry{05/2020}{Master of Science in Analytics}{Georgia Tech}{}{\textit{GPA: 4.0}}{
\begin{itemize}
    \item Machine Learning, Simulation, Data and Visual Analytics, Business Data Analytics, Introduction to Modelling, Introduction to Computing, High Dimensional Data, Regression Analysis
\end{itemize} 
}
\cventry{01/2018}{Micro-Masters in Data, Economics, and Development Policy}{MIT}{}{}{
\begin{itemize}
    \item Data Analysis, Economics, Experimental Design, and Policy Analysis
\end{itemize} 
}
\cventry{04/2013}{Bachelor of Science (Honors) in Biology}{Kings University}{}{}{
\begin{itemize}
    \item Certificate in International Development Studies
    \item Elected VP of Students’ Association
    \item Laurence Decore Student Leadership Award from Government of Alberta
    \item Senior Thesis:  \href{https://www.sciencedirect.com/science/article/abs/pii/S0168160512005065}{Survival of murine norovirus and F-RNA coliphage MS2 on pork during storage and retail display} published in International Journal of Food Microbiology
\end{itemize} 
}
\clearpage
\section{Experience}
\cventry{07/2021--present}{Principal Data Scientist}{Amgen}{United States}{}{
\begin{itemize}
    \item Leadership \& Strategic Planning:
    \begin{itemize}
        \item Co-lead of AI Taskforce for Obesity \& Weight Management. 
        \item Co-lead of AI Learning Lab for employees across Amgen. 
        \item Data Science lead for AI Taskforce for Global Patient Safety.
        \item Data Science lead for Rare Disease Targeting using AI. 
        \item SME for Data Science and Precision Medicine strategy at Amgen, participating in workshops and taskforces to define the future of precision medicine at Amgen.  
    \end{itemize}
    \item Technical Lead:
    \begin{itemize}
        \item Led the ideation and build process for AI use cases in the obesity pipeline.  
        \item Author of white paper on AI for Clinical Applications in Healthcare.
        \item Tech lead for project to develop competitive intelligence for executives.  Built models for news summarization, question/answering, topic modelling, senitiment analysis, and financial forecasting.  
        \item Helped develop and improve a machine learning pipeline for clinical trial optimization and site selection.
        \item Advised business partners on expansion and roll out of production model for Osteoporosis detection.
        \item Ingested computer vision pipeline for ingesting cell painting images for cell phenotype changes into Amgen's technical processes.- I led the ideation process to develop use cases for data science in obesity trials and am now building the use cases into proof of concepts.  
    \end{itemize}
    \item Collaboration \& Community Building:
    \begin{itemize}
        \item Vice Chair of organizing committee for annual Data Science Symposium at Amgen, quarterly AI Demo Days, and quarterly AI Tech Talks.  
        \item Leader and facilitator of Amgen's mentoring program, streamlined and improved matching process using AI
        \item Mentor and manager of junior staff and ambassador for data science across Amgen, facilitating symposiums, journal clubs, knowledge sharing sessions, pilots, and lunch and learns.  
    \end{itemize}
\end{itemize}
}
\cventry{03/2021--07/2021}{Data Scientist 2}{Parsyl}{United States}{}{
\begin{itemize}
    \item Built and deployed model for predicting location of health facility using IOT devices.  
    \item Built algorithm for predicting shelf life lost for muscle meat products in the cold chain
\end{itemize} 
}
\cventry{04/2020--03/2021}{Data Scientist}{HCA Healthcare}{United States}{}{
\begin{itemize}
    \item Modelled ICU capacity, COVID-19 hospitalizations, \& hospital health status.
    \item Built end-to-end pipeline for calculating regional COVID-19 $R_{t}$ values.
    \item Built and deployed predictive models for cost of hospital visit for a patient.
\end{itemize} 
}
\cventry{06/2018--04/2020}{Data Science Co-Op}{Johnson \& Johnson}{United States}{}{
\begin{itemize}
    \item Created product to model anomalous orders for controlled pharmaceuticals, utilized daily by the controlled substance compliance team
    \item Modelled and predicted promotion timing and efficacy for seasonal consumer products
\end{itemize} 
}
\cventry{09/2014--10/2017}{Monitoring and Evaluation Officer}{Mennonite Central Committee}{Zambia}{}{
\begin{itemize}
    \item Applied statistical procedures for evaluating programs and maintaining indicator statistics
    \item Managed 17 different projects and corresponding monitoring strategies and evaluations
\end{itemize} 
}



\end{document}